Model

### 2019-09-17 stats/kids_combination.Rmd
draft model comparison

>>>>

```{r}
fixef <- as_tibble(readRDS("../saves/fixef_brm_model_item_random_only.rds"), rownames = "term")

ranef <-  readRDS("../saves/ranef_brm_model_item_random_only.rds")

model_plot <- bind_rows(
  as_tibble(ranef$familiar, rownames = "familiar")%>%
  mutate(condition = "congruent",
         condition_code = 0),
  as_tibble(ranef$familiar, rownames = "familiar")%>%
  mutate(condition = "incongruent",
         condition_code = 1))%>%
  mutate(grand_intercept = fixef%>%filter(term=="Intercept")%>%pull(Estimate),
         grand_age = fixef%>%filter(term=="age_num")%>%pull(Estimate),
         grand_cond = fixef%>%filter(term=="conditionincongruent")%>%pull(Estimate),
         grand_intact = fixef%>%filter(term=="age_num:conditionincongruent")%>%pull(Estimate))%>%
  group_by(familiar, condition, condition_code) %>%
  expand(Estimate.Intercept,Estimate.conditionincongruent,Estimate.age_num,`Estimate.age_num:conditionincongruent`,grand_intercept,grand_age,grand_cond,grand_intact,age = d$age_num - mean(d$age_num))%>%
  mutate(y = plogis(grand_intercept + 
                      Estimate.Intercept +
                      grand_cond * condition_code +
                      Estimate.conditionincongruent * condition_code +
                      grand_age * age +
                      Estimate.age_num * age +
                      grand_intact * (condition_code * age) +
                      `Estimate.age_num:conditionincongruent` * (condition_code * age)),
         age = age+mean(d$age_num))%>%
  left_join(aoa_ratings%>%mutate(familiar = familiarObject))%>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(familiar), mean_aoa))

ggplot(model_plot, aes(x=age,y = y, col = familiar))+
  geom_hline(yintercept = 0.5, lty=2)+
  geom_line(size = 1)+
  ggtitle("Model")+
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(~condition)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d(name = "familiar object")
```

### 2019-09-17 stats/model.Rmd
draft model comparison

sem_know_model <- readRDS("../saves/sem_know_model_variant3_100k.rds")

@@

```{r}
novel_bm <- readRDS("../saves/novelty_model.rds")

@@

        var modelPredictions = pragmaticListener({label: "novel_word"}, prior, speakerOptimality, sem_knowledge)

@@

@@

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
  data = list(data = me_model_data, comb_data = data_comb_log),
  data_var = "dataFromR",
  model_var = "model",
  chains = 3,
  cores = 3,
  inference_opts = list(method = "incrementalMH",
                        samples = 100000,
                        burn = 50000,
                        verbose = T,
                        lag = 1,
                        verboseLag = 1000)
)

@@

log_like<- sem_know_model %>%
  separate(Parameter, into = c("parameter", "item","age","alignment"), sep = ",")%>%
  filter(parameter == "log_like")%>%
  separate(value, into = c("na", "log_like"),sep = ",")%>%
  select(-na, -item, -age, -alignment)%>%
  mutate(log_like =as.numeric(str_remove(log_like,"[)]")))%>%
  group_by(Chain)%>%
  summarize(logP = logSumExp(log_like))

>>>>

sem_know_model <- readRDS("../saves/sem_know_model_variant3_100k_log_like.rds")

@@

@@

var all_log_likes_prag = map(function(row) { 
      var prior = [row.prior, 1-row.prior]
        var itemLineParameters = all_item_parameters[row.item]
        var sem_knowledge = logistic(itemLineParameters.intercept + 
            itemLineParameters.slope * row.age)

     var speakerOptimality = speakerOptimalityParameters.intercept  + speakerOptimalityParameters.slope * row.age

        var pragModelPredictions = pragmaticListener({label: "novel_word"}, prior, speakerOptimality, sem_knowledge)

        return pragModelPredictions.score(row.correct)

@@

  var log_likelihood_prag = sum(all_log_likes_prag)
  query.add(["log_like", "pragmatics", "NA"], ["NA", log_likelihood_prag])

var all_log_likes_flat = map(function(row) { 
      var prior = [row.prior, 1-row.prior]
        var itemLineParameters = all_item_parameters[row.item]
        var sem_knowledge = logistic(itemLineParameters.intercept + 
            itemLineParameters.slope * row.age)

     var speakerOptimality = speakerOptimalityParameters.intercept  + speakerOptimalityParameters.slope * row.age

        var flatModelPredictions = pragmaticListener({label: "novel_word"}, [.5, .5], speakerOptimality, sem_knowledge)

        return flatModelPredictions.score(row.correct)

  var log_likelihood_flat = sum(all_log_likes_flat)
  query.add(["log_like", "flat_prior", "NA"], ["NA", log_likelihood_flat])

@@

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
  data = list(data = me_model_data, comb_data = data_comb_log),
  data_var = "dataFromR",
  model_var = "model",
  chains = 3,
  cores = 3,
  inference_opts = list(method = "incrementalMH",
                        samples = 100,
                        burn = 100,
                        verbose = T,
                        lag = 1,
                        verboseLag = 1000)
)

@@

log_like<- sem_know_model %>%
  separate(Parameter, into = c("parameter", "model","age","alignment"), sep = ",")%>%
  filter(parameter == "log_like")%>%
  separate(value, into = c("na", "log_like"),sep = ",")%>%
  select(-na, -age, -alignment)%>%
  mutate(log_like =as.numeric(str_remove(log_like,"[)]")))%>%
  group_by(model,Chain)%>%
  summarize(logP = logSumExp(log_like))
